Fractional Types

### 2019-11-22 fracGC/p.tex
small edits to section 6

\paragraph*{Quantum Error Correction.}
Quantum error correction requires the ability to replicate the state of a
qubit onto a number of qubits~\cite[Ch.~3]{NAP25196}. This is impossible to do
directly, by the no-cloning
theorem~\cite{park1970concept,wootters1982single,dieks1982communication}. Again
ancilla qubits solve the problem: because they start in a known
initial state, it is possible to create a simple circuit that makes
their output state match a protected qubit without knowing or
disturbing the protected qubit. Chong et al.~\cite{sigarchblog}
illustrate the idea with a simple example:
\begin{quote}
Consider a 3-qubit quantum majority code in which a logical ``0'' is
encoded as ``000'' and a logical ``1'' is encoded as ``111.''  Just as with
a classical majority code, a single bit-flip error can be corrected by
restoring to the majority value.  Unlike a classical code, however, we
cannot directly measure the qubits else their quantum state will be
destroyed.  Instead, we measure syndromes from each possible pair of
qubits by interacting them with an ancilla, then measure each ancilla.
Although the errors to the qubits are actually continuous, the effect
of measuring the ancilla is to discretize the errors, as well as
inform us whether an error occurred so that it can be corrected.
\end{quote}

\paragraph*{Deferring Quantum Measurements.} The evolution of a
quantum system is deterministic. Measurement adds significant
complications, collapsing the quantum state, and producing
probabilistic results. However, using ancilla qubits, it is possible to
avoid doing any intermediate measurements in a quantum
circuit~\cite{dewolf}.

>>>>

\paragraph*{Quantum Error Correction.}
Quantum error correction requires the ability to replicate the state of a
qubit onto a number of qubits~\cite[Ch.~3]{NAP25196}. This is impossible to do
directly, by the no-cloning
theorem~\cite{park1970concept,wootters1982single,dieks1982communication}. Again
ancilla qubits solve the problem: because they start in a known
initial state, it is possible to create a simple circuit that makes
their output state match a protected qubit without knowing or
disturbing the protected qubit. Chong et al.~\cite{sigarchblog}
illustrate the idea with a simple example:
\begin{quote}
Consider a 3-qubit quantum majority code in which a logical ``0'' is
encoded as ``000'' and a logical ``1'' is encoded as ``111.''  Just as with
a classical majority code, a single bit-flip error can be corrected by
restoring to the majority value.  Unlike a classical code, however, we
can not directly measure the qubits else their quantum state will be
destroyed.  Instead, we measure syndromes from each possible pair of
qubits by interacting them with an ancilla, then measure each ancilla.
Although the errors to the qubits are actually continuous, the effect
of measuring the ancilla is to discretize the errors, as well as
inform us whether an error occurred so that it can be corrected.
\end{quote}

\paragraph*{Deferring Quantum Measurements.} The evolution of a
quantum system is deterministic. Measurement add significant
complications, collapsing the quantum state, and producing
probabilistic results. However, using ancilla qubits it is possible to
avoid doing any intermediate measurements in a quantum
circuit~\cite{dewolf}.
